---
title: "Vehicle MPG Prediction Application"
author: "Ignas"
date: "20/04/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Overview

This presentation and Shinny application was build for the course Developing Data Products.

The Shiny app developed for this assignment is available at: <https://spogisignas.shinyapps.io/Final/>

The source codes of ui.R and server.R are available on the GitHub:
<https://github.com/Spogislavas/Developing-data-products>

## Idea

The idea of this application is to use previously constructed multivariable model in order to determine the MPG by selecting weight, transmission type and how fast vehicle reach 1/4 mile. 

## Dataset {.smaller}
For this application build, `mtcars` data set was used. Summary of the data set:
```{r}
summary(mtcars)
```

## Model

Fitted model used in the application is: mpg as the outcome while am, wt and qsec as predictors. Coefficients are presented below.

```{r}
lm(mpg ~ am + wt + qsec, data = mtcars)
```
